---
title: "datasauRus"
author: "Kasia Banas"
date: "2024-09-26"
output: html_document
---

Install and load the datasauRus library:

```{r}
install.packages("datasauRus")
library(datasauRus)
```

Load the tidyverse: 
```{r}
library(tidyverse)
```

`datasaurus_dozen` is a dataset demonstrating the utility of visualization. 
These 12 datasets are equal in standard measures: mean, standard deviation, 
and Pearson's correlation. But they look very different
Run the chunk below to get more info about this dataset:

```{r}
?datasaurus_dozen
```

See what datasets are in the datasaurus_dozen:

```{r}
datasaurus_dozen %>% 
  distinct(dataset)
```

## Exercise 1
#Pick 2 datasets and plot them next to one another
#(I'd recommend scatterplot, use facets if you like)

#Filter Content
dinobullseye <- datasaurus_dozen %>%
     filter(dataset %in% c("dino", "bullseye"))

dinobullseye

#Plot only Dino & Bullseye side-by-side
dinobullseye %>%
    ggplot(aes(x = x, y = y, colour = dataset)) +
    geom_point() +
    facet_wrap (~dataset)

#Plot all side-by-side
datasaurus_dozen %>%
    ggplot(aes(x = x, y = y, colour = dataset)) +
    geom_point() +
    facet_wrap (~dataset)


## Exercise 2
For these same two datasets, find the mean and standard deviation
for the x and y variable in each. What did you find? 

datasaurus_dozen %>%
      filter(dataset %in% c("dino", "bullseye")) %>%
      group_by(dataset) %>%
      summarise(mean_x = mean(x), sd_x = (sd(x)), mean_y = mean(y), sd_y = sd(y))
      

